Simulation Study: Varying Null Proportion

### 2018-06-07 datasets/simulations/simulations-varyingpi0.Rmd
Add lower pi0 values in simulations

## intermediary files we create below
null80_file <- file.path(resdir, "varyingpi0-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-benchmark-nullprop99.rds")

@@

@@

First, we consider the setting where 80% of tests are null.

>>>>

## intermediary files we create below
null05_file <- file.path(resdir, "varyingpi0-benchmark-nullprop05.rds")
null10_file <- file.path(resdir, "varyingpi0-benchmark-nullprop10.rds")
null20_file <- file.path(resdir, "varyingpi0-benchmark-nullprop20.rds")
null50_file <- file.path(resdir, "varyingpi0-benchmark-nullprop50.rds")
null80_file <- file.path(resdir, "varyingpi0-benchmark-nullprop80.rds")
null90_file <- file.path(resdir, "varyingpi0-benchmark-nullprop90.rds")
null95_file <- file.path(resdir, "varyingpi0-benchmark-nullprop95.rds")
null99_file <- file.path(resdir, "varyingpi0-benchmark-nullprop99.rds")

@@

# 5% Null Setting

First, we consider the setting where 5% of tests are null.

```{r null05-parameters}
pi0 <- pi0_sine(0.05)             # numeric: proportion of null hypotheses
seed <- 1010
```

```{r null05-run-simulation}
if (file.exists(null05_file)) {
    res <- readRDS(null05_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null05_file)
}
```

```{r null05-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null05-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null05-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null05-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null05-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null05-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

# 10% Null Setting

Next, we consider the setting where 10% of tests are null.

```{r null10-parameters}
pi0 <- pi0_sine(0.10)             # numeric: proportion of null hypotheses
seed <- 1201
```

```{r null10-run-simulation}
if (file.exists(null10_file)) {
    res <- readRDS(null10_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null10_file)
}
```

```{r null10-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null10-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null10-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null10-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null10-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null10-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

# 20% Null Setting

Next, we consider the setting where 20% of tests are null.

```{r null20-parameters}
pi0 <- pi0_sine(0.20)             # numeric: proportion of null hypotheses
seed <- 51
```

```{r null20-run-simulation}
if (file.exists(null20_file)) {
    res <- readRDS(null20_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null20_file)
}
```

```{r null20-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null20-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null20-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null20-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null20-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null20-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

# 50% Null Setting

Next, we consider the setting where 50% of tests are null.

```{r null50-parameters}
pi0 <- pi0_sine(0.50)             # numeric: proportion of null hypotheses
seed <- 500
```

```{r null50-run-simulation}
if (file.exists(null50_file)) {
    res <- readRDS(null50_file)
} else {
    res <- mclapply(X = 1:B, FUN = simIteration, bench = bdplus, m = m,
                    pi0 = pi0, tstat = tstat, icovariate = icovariate,
                    tstat_dist = tstat_dist, null_dist = null_dist,
                    seed = seed, mc.cores = cores)
    saveRDS(res, file = null50_file)
}
```

```{r null50-one-simulation}
onerun <- simIteration(bdplus, m = m, pi0 = pi0, tstat = tstat, tstat_dist = tstat_dist,
                       icovariate = icovariate, null_dist = null_dist, execute = FALSE)
```

```{r, null50-diag-scatter, results = "hide", fig.width=4.5, fig.height=3.5}
rank_scatter(onerun, pvalue = "pval", covariate = "ind_covariate")
```

```{r, null50-diag-hist, results = "hide", fig.width=10, fig.height=3.2}
strat_hist(onerun, pvalue = "pval", covariate = "ind_covariate", maxy = 5, numQ = 3)
```

```{r null50-metrics-averages, results = "hide"}
resdf <- plotsim_standardize(res, alpha = seq(0.01, 0.10, 0.01))

```{r null50-metrics-covlineplot, results = "hide"}
covariateLinePlot(res, alpha = ualpha, covname = "effect_size")

```{r null50-metrics-upset, results = "hide"}
if (numberMethodsReject(resdf, alphacutoff = ualpha, filterSet = excludeSet) >= 3) {
    aggupset(res, alpha = ualpha, supplementary = FALSE, return_list = FALSE)
} else {
    message("Not enough methods found rejections at alpha ", ualpha, 
            "; skipping upset plot")
}
```

@@

Next, we consider the setting where 80% of tests are null.
